% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

% Adapted for/by Chaulio Ferreira in 2018

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill

% added by Chaulio Ferreira:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage[brazil]{babel}
\usepackage{ragged2e} % to justify text
\usepackage{bibentry}



%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{2pt} %ORIGINALLY 8pt
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-11pt} %ORIGINALLY -5pt
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Chaulio Ferreira} & \textbf{\today} \\
PhD candidate at the Technical University of Munich & chauliof@gmail.com \\
http://github.com/chaulio/CV & chaulio.ferreira@tum.de \\


\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{About}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\justify
~~~~~~PhD candidate at the Chair for Scientific Computing of the Technical University of
Munich since 2015. Working on performance optimization of PDE engines with parallel adaptive mesh refinement, especially on Riemann solvers for the shallow water equations.
He has expertise mostly in the following areas: Design and Analysis of Algorithms; Data Structures; Geographical Information Science; High Performance Computing.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item	\ressubheading{Technical University of Munich}{Munich, Germany}{PhD candidate at the chair for Scientific Computing}{Oct 2015 -- ongoing}

	\ifdef{\completeversion} {
	  \begin{itemize}
	    \resitem{Title: \emph{Vectorization of Riemann solvers for the single- and multi-layer shallow water equations}}
	    \resitem{Supervisor: Michael Bader}
	    %\resitem{Grants from: CPNq (Brazil)}
	  \end{itemize}
	}
	
\item	\ressubheading{Columbia University}{New York, USA}{Visiting scholar}{Sep 2017 -- Nov 2017}
	
	\ifdef{\completeversion} {
	  \begin{itemize}
	    \resitem{Guest at the Department of Applied Physics and Applied Mathematics}
	    \resitem{Supervisor: Kyle T. Mandli}
	    %\resitem{Grants from: TUM Graduate School (Germany)}
	  \end{itemize}
	}


\item	\ressubheading{Federal University of Viçosa}{Viçosa, Brazil}{Master's degree in Computer Science}{Mar 2012 - Feb 2014}


	\ifdef{\completeversion} {
	  \begin{itemize}
	    \resitem{Title: \emph{Visibility maps in large terrains represented by regular grids}}
	    \resitem{Supervisor: Marcus Vinicius Alvim Andrade}
	    \resitem{Co-supervisor: Salles Viana Gomes de Magalhães}
	    %\resitem{Grants from: CAPES (Brazil)}
	  \end{itemize}
	 }
	
\item	\ressubheading{Federal University of Viçosa}{Viçosa, Brazil}{Bachelor's degree in Computer Science}{Mar 2008 - Jan 2012}

	\ifdef{\completeversion} {
	  \begin{itemize}
	    \resitem{Final project: \emph{An interactive system to site observers in terrains represented by digital elevation models}}
	    \resitem{Supervisor: Marcus Vinicius Alvim Andrade}
	  \end{itemize}
	 }

\end{itemize}



\ifdef{\completeversion} {
  %\newpage
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional Activities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item
	\ressubheading{Federal University of Viçosa}{Viçosa, Brazil}{Lecturer at the Department of Informatics}{Apr 2014 -- Jul 2015}
	\begin{itemize}
	  \ifdef{\completeversion}{
	    \resitem{Courses:}
	    \begin{itemize}
	      \item (INF 100) Introduction to programming I
	      \item (INF 101) Introduction to programming II
	      \item (INF 110) Programming I
	      \item (INF 213) Data structures
	      \item (INF 390) Computer graphics
	      \item (INF 492) Programming challenges
	    \end{itemize}
	  }
	  { %else (short version)
	    \item Courses: Data structures, Computer Graphics and various Programming courses.
	  }
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \item \textbf{Languages:} Fluent in English and Portuguese. Basic knowledge of German and Spanish.
  \item \textbf{Development:} C/C++, Fortran, Python, Java.
  \item \textbf{High Performance Computing:} MPI, OpenMP, vectorization, CUDA.
  \item \textbf{Other:} Git, OpenGL, Linux, Windows, \LaTeX.
\end{itemize}


\ifdef{\completeversion}
{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \resheading{Awards}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{itemize}
    \item Best paper award at the XIV Brazilian Symposium on Geonfirmatics -- ``A parallel sweep line algorithm for visibility computation'' (Brazilian Institute of Spatial Research, 2013).
    \item Honor certificate for Excellent Academic Performance (Federal University of Viçosa, Brazil, 2012).
    \item Silver Medal at the 1st Programming Marathon of the State of Minas Gerais, Brazil (Brazilian Computing Society, 2012)
    \item Fourth place at the 7th Marathon of Parallel Programming (Technical Committee on Computer Architecture and High Performance Computing -- Brazilian Computing Society, 2012).
    \item First place at the regional stage of the International Collegiate Programming Contest (Juiz de Fora, Brazil, Association for Computing Machinery, 2012).
    \item 28th place at the national stage of the International Collegiate Programming Contest (Londrina, Brazil, Association for Computing Machinery, 2012).
    \item Second place at the 6th Marathon of Parallel Programming (Technical Committee on Computer Architecture and High Performance Computing -- Brazilian Computing Society, 2011).
    \item First place at the 2nd GPU Programming Contest (Technical Committee on Computer Architecture and High Performance Computing -- Brazilian Computing Society, 2011).
    \item First place at the regional stage of the International Collegiate Programming Contest (Juiz de Fora, Brazil, Association for Computing Machinery, 2010).
    \item 25th place at the national stage of the International Collegiate Programming Contest (Joinville, Brazil, Association for Computing Machinery, 20120.
  \end{itemize}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \resheading{Publications}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \nobibliography{publications}
  \bibliographystyle{IEEEtran}

  %\begin{itemize}
  ~~~  \textbf{Journal papers:}
    \begin{enumerate}
    \item \bibentry{ferreira2016efficient}
    \item \bibentry{ferreira2014parallel}
    \end{enumerate}

  ~~~  \textbf{Conference papers:}

    \begin{enumerate}
    \item \bibentry{ferreira2017load}
    \item \bibentry{pena2014efficient}
    \item \bibentry{pena2014improved}
    \item \bibentry{ferreira2013parallel}
    \item \bibentry{pena2013algoritmo}
    \item \bibentry{ferreira2012more}
    \item \bibentry{jacob2012gpu}
    \item \bibentry{ferreira2012abordagem}
    \item \bibentry{ferreira2011sistema}
    \item \bibentry{de2010heuristics}
    \end{enumerate}


  \newpage
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \resheading{Scientific talks}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{enumerate}
    \item ``Load balancing and patch-based parallel adaptive mesh refinement for Tsunami simulation on heterogeneous platforms using Xeon Phi coprocessors'', at \emph{Platform for Advanced Scientific Computing} (PASC), in Lugano, Switzerland, 2017.
    \item ``Performance and Time to Solution of Dynamically Adaptive Tsunami Simulations'', at \emph{SIAM Conference on Computational Science and Engineering} (SIAM CSE), in Atlanta, USA, 2017.
    \item ``Dynamically adaptive tsunami simulations on Xeon Phi architectures'', at \emph{Congress of the Italian Society of Industrial and Applied Mathematics} (SIMAI), in Milan, Italy, 2016.
    \item ``GPU optimization techniques applied to Scale Free Gene Regulatory Networks based on Threshold Function'', at \emph{13th Symposium
  on Computer Systems} (WSCAD-SSC), in Petropolis, Brazil, 2012.
  \end{enumerate}
}
{ % else (short version)
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \resheading{Awards and academic production}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
  \begin{itemize}
   \item 10 awards, including best conference paper, honor certificate for academic performance and various programming competitions.
   \item 2 papers published in peer-reviewed journals as first author.
   \item 10 papers published in conferences, 5 of them as first author.
   \item 4 scientific talks in international conferences in the US, Switzerland, Italy and Brazil.
   \item Complete lists are available in the complete version of this CV, at [link].
  \end{itemize}

  
}

\end{document}
